\bf Title

### 2023-12-11 article/paper_padic_spec.tex
petites corrections prop 6.1

\begin{proposition}
Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
be a linear mapping. Then $f(\PP)$ is a polyhedron.
\end{proposition}
\begin{proof}
Let us assume that 
$\PP$ is defined by the set of conditions $\left\lbrace \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
finite set $I \subset \N$ and all $l_i \in K[X]_1$ for $i \in I.$
We further assume that $\PP$ is non-empty.

@@

We first prove the result when $f$ is in $\GL_n(\OK)$.
In that case, $x \in f(P)$ if and only if for all
$i \in I,$
$\val (l_i (f^{-1}(x)) \geq 0$.
The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
and $f(P)$ is a polyhedra.

@@

We can computer a Smith Normal Form
of the $q \times (n-1)$ matrix defined by the 
$n-1$ first columns of $A$
to obtain a decomposition of the form:
\[ Q_A A P_A^{-1} = \begin{bmatrix}
\delta_1	& 		& 			&   &		 &  &a_1	\\
			& \ddots& 			& 0	&		 &	&		\\
			&		& \delta_l  &   & 		 &	&		\\
			&		&			&0  & 		 &	& 		\\
			&		&			&   & \ddots &	&		\\
			&		&			&	&		 & 0&a_{n-1} \\
			&		&			&	&		 &	&a_n 	\\
			&		&			&	&		 &	&    	\\
			&		&			&	&		 &	&a_q 	\\			
\end{bmatrix},\]
with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$

>>>>

\begin{proposition}
Let $\PP \subset K^n$ be a polyhedron and $f: K^n \rightarrow K^m$
be a linear mapping. Then $f(\PP)$ is a polyhedron.
\end{proposition}
\begin{proof}
Let us assume that 
$\PP = \left\lbrace x \in K^n : \val (l_i (x) ) \geq 0, \textrm{ for } i \in I \right\rbrace$ for some
finite set $I \subset \N$ and $l_i \in K[x]_1$, for $i \in I.$ We further assume that $\PP \neq \emptyset$.

@@

We first prove the result when $f$ is in $\GL_n(\OK)$.
In that case, $x \in f(P)$ if and only if for all
$i \in I,$
$\val (l_i (f^{-1}(x)) \geq 0$.
The $l_i \circ f^{-1}$ are clearly in $K[x]_1$
and $f(P)$ is a polyhedron.

@@

We can compute a Smith Normal Form
of the $q \times (n-1)$ matrix defined by the 
$n-1$ first columns of $A$
to obtain a decomposition of the form:
\[ Q_A A P_A^{-1} = \begin{bmatrix}
\delta_1	& 		& 			&   &		 &  &a_1	\\
			& \ddots& 			& 0	&		 &	&		\\
			&		& \delta_l  &   & 		 &	&		\\
			&		&			&0  & 		 &	& 		\\
			&		&			&   & \ddots &	&		\\
			&		&			&	&		 & 0&a_{n-1} \\
			&		&			&	&		 &	&a_n 	\\
			&		&			&	&		 &	&    	\\
			&		&			&	&		 &	&a_q 	\\			
\end{bmatrix},\]
with $Q_A \in \GL_q(\OK)$ and $P_A \in \GL_n(\OK)$ such that $P_A(e_n)=e_n.$
